Automated iterative forecasting for the Portal Project

### 2018-02-02 manuscript/portal_iterative_forecasting_ms.Rmd
Fix typo

Because iterative near-term forecasting requires a dynamic interplay of models, predictions, and data, Dietze et al [-dietze2018] highlight approaches to data management, model construction and evaluation, and cyberinfrastructure that are necessary to effectively implement this type of forecasting (Box 1). Data to be used for iterative near-term forecasting needs to be widely accessible, which requires data to be released quickly under open licenses [@dietze2018; @vargas2017] and structured so that it can be used easily by a variety of researchers and in multiple modeling approaches [@borer2009; @strasser2011]. Models need to be able to deal with uncertainty, in the predictors and the predictions, to properly convey uncertainty in the resulting forecasts [@diniz-filho2009]. Multiple models should be developed, both to assess which models are performing best [@dietze2018] and to facilitate combining models to form ensemble predictions which tend to form better than single models [@araujo2007; @diniz-filho2009]. Ensuring that data and models are regularly updated and new forecasts are made requires cyberinfrastructure to automate data processing, model fitting, prediction, model evaluation, forecast visualization, and archiving. In combination, these approaches should allow forecasts to be easily rerun and evaluated as new data becomes available [Box 1; @dietze2018].

>>>>

Because iterative near-term forecasting requires a dynamic interplay of models, predictions, and data, Dietze et al [-dietze2018] highlight approaches to data management, model construction and evaluation, and cyberinfrastructure that are necessary to effectively implement this type of forecasting (Box 1). Data to be used for iterative near-term forecasting needs to be widely accessible, which requires data to be released quickly under open licenses [@dietze2018; @vargas2017] and structured so that it can be used easily by a variety of researchers and in multiple modeling approaches [@borer2009; @strasser2011]. Models need to be able to deal with uncertainty, in the predictors and the predictions, to properly convey uncertainty in the resulting forecasts [@diniz-filho2009]. Multiple models should be developed, both to assess which models are performing best [@dietze2018] and to facilitate combining models to form ensemble predictions which tend to perform better than single models [@araujo2007; @diniz-filho2009]. Ensuring that data and models are regularly updated and new forecasts are made requires cyberinfrastructure to automate data processing, model fitting, prediction, model evaluation, forecast visualization, and archiving. In combination, these approaches should allow forecasts to be easily rerun and evaluated as new data becomes available [Box 1; @dietze2018].
